---
title: Building a Macroeconomic Model of Taiwan
author: Travis Dorsey
date: '2020-05-26'
slug: macroeconomic-model-of-taiwan
bibliography: econ_models_bib.bib
biblio-style: "apalike"
nocite: |
  @jp_gnp
  @tfp_dat
output:
  blogdown::html_page:
    toc: true
    toc_depth: 2
    number_sections: true
categories: [Econometric Models]
tags:
  - economics
  - data
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)

library(tidyverse)
library(kableExtra)
library(equatiomatic)
library(systemfit)
library(lubridate)

options(scipen=999)

econ_vars <- read_csv("/Users/sharedcomputer/MMT in Taiwan/Analysis Replication Files/Macroeconomic Model of Taiwan/New Variable List.csv")

get_model_formula <- function(model_eq) {
  eq_formula <- deparse(model_eq$terms)

  test_coef <- as.data.frame(model_eq$coefficients) %>%
    rownames_to_column(var = "variable_name")
  
  new_rhs <- test_coef %>%
    mutate(rn = row_number()) %>%
    group_by(rn) %>%
    mutate(variable_name = clean_var_names(variable_name)) %>%
    ungroup() %>%
    select(-rn) %>%
    mutate(rhs = ifelse(variable_name == "(Intercept)", 
                        round(Estimate, 4), 
                        paste(round(Estimate, 4), variable_name, sep = "*"))) %>%
    mutate(rhs = str_remove_all(rhs, "`"))
  new_rhs <- str_c(new_rhs$rhs, collapse = " + ")
  new_lhs <- str_replace(str_sub(eq_formula, 1, str_locate(eq_formula, "~")[1]), "~", "=")
  new_lhs <- str_remove_all(new_lhs, "`")
  new_lhs <- clean_var_names(new_lhs)
  
  new_eq <- paste(new_lhs, new_rhs)
  return(new_eq)
}

clean_var_names <- function(eqn_text) {
  div_detect <- str_detect(eqn_text, "_d_")
  eq_detect <- str_detect(eqn_text, " =")
  
  if(div_detect){
    if(eq_detect){
      eqn_text <- str_replace_all(eqn_text, " =", "")
      eqn_text <- str_split(eqn_text, "_d_")
      eqn_text <- sprintf("\\frac{%s}{%s}", eqn_text[[1]][1], eqn_text[[1]][2])
      eqn_text <- paste(eqn_text, "= ")
    } else{
      eqn_text <- str_split(eqn_text, "_d_")
      eqn_text <- sprintf("\\frac{%s}{%s}", eqn_text[[1]][1], eqn_text[[1]][2])
    }
  }
  
  eqn_text <- str_replace_all(eqn_text, "_x_", " * ")
  eqn_text <- str_replace_all(eqn_text, "_m_", " - ")
  eqn_text <- str_replace_all(eqn_text, "_p_", " + ")
  eqn_text <- str_replace_all(eqn_text, "_1", "_{-1}")
  
  return(eqn_text)
}

```


Following the methodology laid out by the [Directorate-General of Budget, Accounting, and Statistics](https://www.stat.gov.tw/public/Attachment/6531914262FZ3FA2L.pdf)^[@dgbas_econ], I build an econometric model of Taiwan's macroeconomy that I can utilize to test the impact of policy proposals as in [Fullwiler (2006)](simulating_jg_us).^[@simulating_jg_us] This approach is based on the Cowles Commission methodology of simultaneous equations (similar to the well known [Fairmodel](https://fairmodel.econ.yale.edu/mmm2/mm2018.pdf)^[@fairmodel] used to study the US economy and that of [Lin (2007)](http://www.econ.ntu.edu.tw/ter/new/data/new/TER38-1/TER381-1.pdf)^[@lin_2007_tw_macro] which models the Taiwanese economy) and has been shown to outperform VAR and other time series approaches for macroeconomic forecasts, while also providing a more useful framework for testing policy options than dynamic stochastic generalized equilibrium models, which have [their own issues](https://www.federalreserve.gov/econresdata/ifdp/2016/files/ifdp1175.pdf).^[@frb_dsge] 


***
# Variables and Equations
The model will consist of 25 simultaneous equations, with 38 endogenous variables and 24 exogenous variables.

## Variables 

### Endogenous Variables
```{r endog_vars}
econ_vars %>%
  filter(Exogenous == "N") %>%
  select(-c(Description_zh, Exogenous, `Equations Used`)) %>%
  kable('html', align = c("l", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, font_size = 12) %>%
  row_spec(0, bold = TRUE, background = "grey", color = "white") 
```

### Exogenous Variables
```{r exog_vars}
econ_vars %>%
  filter(Exogenous == "Y") %>%
  select(-c(Description_zh, Exogenous, `Equations Used`)) %>%
  kable('html', align = c("l", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, font_size = 12) %>%
  row_spec(0, bold = TRUE, background = "grey", color = "white") 
```


## Equations
Here I show the equations that make up this macroeconometric model of Taiwan.

### Commodity Market
Real Private Consumption (C):
$$
C = f(\underset{+}{C_{-1}}, \underset{+}{\frac{YDD^{nominal}}{PGDP}}, \underset{+}{\frac{STKVLE^{nominal}}{CPI}})
$$
Real Private Fixed Investment (IBF):
$$
IBF = f(\underset{+}{IBF_{-1}}, \underset{+}{IG_{-1}}, \underset{-}{TDR1Y - @PCHY(CPI)},\\ \underset{+}{EXG_{-1}},
\underset{+}{\frac{STKVLE^{nominal}}{CAPSTOCK^{nominal}}})
$$

Real Exports of Goods, Transportation, and Insurance (EXG):
$$
EXG = f(\underset{-}{\frac{PX}{WPX * RX}}, \underset{+}{GDPMAJOR}, \underset{+}{ICSALES^{nominal}},\\
\underset{+}{SPIKE2002}, \underset{-}{STEP2008})
$$

Real Other Exports (EXS):
$$
EXS = f(\underset{+}{EXS_{-1}}, \underset{+}{OVERSEAREV^{nominal}},\\ \underset{+}{VISITORS}, \underset{+}{RX})
$$
Real Imports of Goods, Transportation, and Insurance (IMG):
$$
IMG = f(\underset{+}{EXG}, \underset{+}{C}, \underset{+}{IPC + IBF + JJ})
$$
Real Other Imports (IMS):
$$
IMS = f(\underset{+}{IMS_{-1}}, \underset{+}{OUTBOUND})
$$

### Price Indices

Import Price Index (PM):
$$
PM = f(\underset{+}{RX}, \underset{-}{JPNRX}, \underset{+}{NONFUEL},\\ \underset{+}{POIL}, \underset{+}{WPX})
$$

Export Price Index (PX):
$$
PX = f(\underset{+}{RX}, \underset{+}{PM}, \underset{+}{WTVG})
$$

Domestic Production Price Index (PD):
$$
PD = f(\underset{+}{PD_{-1}}, \underset{+}{PM}, \underset{+}{GDP}, \underset{+}{SPIKE2008})
$$

Food Consumer Price Index (PF):
$$
PF = f(\underset{+}{PF_{-1}}, \underset{+}{FOOD}, \underset{+}{WG^{nominal}_{-1}}, \underset{+}{TYPH_T})
$$
Non-Food Consumer Price Index (PO):
$$
PO = f(\underset{+}{PO_{-1}}, \underset{+}{PM_{-1}}, \underset{+}{PM}, \underset{+}{WG^{nominal}})
$$

Private Consumption Deflator (PC):
$$
PC = f(\underset{+}{PF}, \underset{+}{PO})
$$

Government Consumption Deflator (PCG):
$$
PCG = f(\underset{+}{PO}, \underset{+}{WGP}, \underset{+}{PIG})
$$
Private Fixed Investment Deflator (PIBF):
$$
PIBF = f(\underset{+}{PIBF_{-1}}, \underset{+}{PCON}, \underset{+}{PCA},\\ \underset{+}{WGST^{nominal}}, \underset{-}{SPIKE2008})
$$
Government Fixed Investment Deflator (PIG):
$$
PIG = f(\underset{+}{PIG_{-1}}, \underset{+}{PCON}, \underset{+}{WGST^{nominal}}, \underset{-}{SPIKE2008})
$$

Public Enterprise Fixed Investment Deflator (PIPC)
$$
PIPC = f(\underset{+}{PCON}, \underset{+}{PCA}, \underset{-}{SPIKE2008})
$$

Gross Capital Formation Deflator (PGCF):
$$
PGCF = f(\underset{+}{PIBF}, \underset{+}{PIG}, \underset{+}{PIPC})
$$
Exports of Goods and Services Deflator (PEX):
$$
PEX = f(\underset{+}{PX}, \underset{+}{CPI})
$$

Imports of Goods and Services Deflator (PIM):
$$
PIM = f(\underset{+}{PM}, \underset{+}{CPI})
$$

### Financial Money Market
M1B:
$$
\frac{M1B}{CPI} = f(\underset{-}{CPI}, \underset{+}{GDP}, \underset{+}{\frac{VSTOCK^{nominal}}{CPI}},\\ \underset{-}{TDR1Y - NOTERATE})
$$

One-year Fixed Deposit Rate (TDR1Y):
$$
TDR1Y = f(\underset{+}{REQ}, \underset{+}{IR}, \underset{+}{GDP_{-1}})
$$

Total Market Capitalization of Listed Stocks (STKVLE$):
$$
STKVLE$ = f(\underset{+}{M1B}, \underset{+}{VSTOCK^{nominal}}, \underset{-}{SPIKE2009})
$$

### Labor Market

Number of Employed (NE):
$$
NE = f(\underset{+}{NE_{-1}}, \underset{-}{\frac{WG^{nominal}}{CPI}}, \underset{+}{GDP})
$$

Monthly Wages per Worker in Industry and Service Sectors (WG$):
$$
WG^{nominal} = f(\underset{+}{WG^{nominal}_{-1}}, \underset{+}{GDP^{nominal}_{-1} - DEP^{nominal}_{-1}}, \underset{+}{CPI}, \underset{+}{WGP})
$$

### Tax Revenues
Tax Revenues (TAX$):
$$
TAX^{nominal} = f(\underset{+}{GDP^{nominal}_{-1}}, \underset{+}{EX^{nominal}+C^{nominal}},\\ \underset{+}{VSTOCK^{nominal}})
$$


```{r load_econ_data}
lag_1_q <- 1

train_test_cutoff <- as_date("2017-01-01")

vars_to_log <- c("TAX$", "GDP", "GDP$", "C", "C$", "CG", "CG$", "EXG", "EXG$", "EXS", "EXS$", "GCF", "GCF$", 
                 "IMG", "IMG$", "IMS", "IMS$", "IBF", "IBF$", "IG", "IG$", "DEP$", "YDD$", "CAPSTOCK$", "STKVLE$",
                 "VSTOCK$", "M1B", "OUTBOUND", "OVERSEAREV$", "TAX$", "VISITORS")

### Load Dataset
econ_data_url <- "https://raw.githubusercontent.com/dorseytf/Blog-Replication-Scripts/master/Taiwan%20Macro%20Dataset.csv"

econ_data <- read_csv(url(econ_data_url)) %>%
  mutate(across(one_of(vars_to_log), log)) %>%
  mutate(C_1               = lag(C, lag_1_q),
         YDD_d_PGDP        = `YDD$`/PGDP,
         STKVLE_d_CPI      = `STKVLE$`/CPI,
         IBF_1             = lag(IBF, lag_1_q),
         IG_1              = lag(IG, lag_1_q),
         PCHY_CPI          = (CPI - lag(CPI, lag_1_q))/lag(CPI, lag_1_q),
         TDR1Y_m_PCHY_CPI  = TDR1Y - PCHY_CPI,
         EXG_1             = lag(EXG, lag_1_q),
         STKVLE_d_CAPSTOCK = `STKVLE$`/`CAPSTOCK$`,
         PX_d_WPX_x_RX     = PX/(WPX*RX),
         EXS_1             = lag(EXS, lag_1_q),
         IPC_p_IBF_p_JJ    = IPC + IBF + JJ,
         IMS_1             = lag(IMS, lag_1_q),
         PD_1              = lag(PD, lag_1_q),
         PF_1              = lag(PF, lag_1_q),
         `WG$_1`           = lag(`WG$`, lag_1_q),
         PO_1              = lag(PO, lag_1_q), 
         PM_1              = lag(PM, lag_1_q),
         PIBF_1            = lag(PIBF, lag_1_q),
         PIG_1             = lag(PIG, lag_1_q),
         M1B_d_CPI         = M1B/CPI,
         VSTOCK_d_CPI      = `VSTOCK$`/CPI,
         TDR1Y_m_NOTERATE  = TDR1Y - NOTERATE,
         GDP_1             = lag(GDP, lag_1_q),
         NE_1              = lag(NE, lag_1_q),
         WG_d_CPI          = `WG$`/CPI,
         `GDP$_1`          = lag(`GDP$`, lag_1_q),
         `DEP$_1`          = lag(`DEP$`, lag_1_q),
         GDP_m_DEP         = `GDP$_1` - `DEP$_1`,
         EX_p_C            = `EX$` + `C$`) %>%
  filter_all(all_vars(!is.na(.)))

# Commodity Market
c_eqn <- C ~ C_1 + `YDD$` + STKVLE_d_CPI
ibf_eqn <- IBF ~ IBF_1 + IG_1 + TDR1Y_m_PCHY_CPI + EXG_1 + STKVLE_d_CAPSTOCK
exg_eqn <- EXG ~ PX_d_WPX_x_RX + GDPMAJOR + `ICSALES$` + SPIKE2002 + STEP2008
exs_eqn <- EXS ~ EXS_1 + `OVERSEAREV$` + VISITORS + RX
img_eqn <- IMG ~ EXG + C + IPC_p_IBF_p_JJ
ims_eqn <- IMS ~ IMS_1 + OUTBOUND

commodity_eqn <- list(c = c_eqn, ibf = ibf_eqn, exg = exg_eqn, exs = exs_eqn, img = img_eqn, ims = ims_eqn)

# Price Indices
pm_eqn <- PM ~ RX + JPNRX + NONFUEL + POIL + WPX 
px_eqn <- PX ~ RX + PM + WTVG
pd_eqn <- PD ~ PD_1 + PM + GDP + SPIKE2008
pf_eqn <- PF ~ PF_1 + FOOD + `WG$_1` + TYPH_T
po_eqn <- PO ~ PO_1 + PM_1 + PM + `WG$`
pc_eqn <- PC ~ PF + PO
pcg_eqn <- PCG ~ PO + WGP + PIG
pibf_eqn <- PIBF ~ PIBF_1 + PCON + PCA + `WGST$` + SPIKE2008
pig_eqn <- PIG ~ PIG_1 + PCON + `WGST$` + SPIKE2008
pipc_eqn <- PIPC ~ PCON + PCA + SPIKE2008
pgcf_eqn <- PGCF ~ PIBF + PIG + PIPC
pex_eqn <- PEX ~ PX + CPI
pim_eqn <- PIM ~ PM + CPI

price_eqn <- list(pm = pm_eqn, px = px_eqn, pd = pd_eqn, pf = pf_eqn, po = po_eqn, pc = pc_eqn, 
                  pcg = pcg_eqn, pibf = pibf_eqn, pig = pig_eqn, pipc = pipc_eqn, 
                  pgcf = pgcf_eqn, pex = pex_eqn, pim = pim_eqn)

# Financial Money Market
m1b_eqn <- M1B_d_CPI ~ CPI + GDP + VSTOCK_d_CPI + TDR1Y_m_NOTERATE
tdr1y_eqn <- TDR1Y ~ REQ + IR + GDP_1
stkvle_eqn <- `STKVLE$` ~ M1B + `VSTOCK$` + SPIKE2009

fin_eqn <- list(m1bcpi = m1b_eqn, tdr1y = tdr1y_eqn, stkvle = stkvle_eqn)

# Labor Market
ne_eqn <- NE ~ NE_1 + WG_d_CPI + GDP
wg_eqn <- `WG$` ~ `WG$_1` + GDP_m_DEP + CPI + WGP

labor_eqn <- list(ne = ne_eqn, wg = wg_eqn)

# Tax Revenue
tax_eqn <- `TAX$` ~ `GDP$_1` + EX_p_C + `VSTOCK$`

```



```{r fit_models}
macro_eqn_list <- c(commodity_eqn, price_eqn, fin_eqn, labor_eqn, tax = tax_eqn)

macro_iv_list <- ~ `CAPSTOCK$` + GDPMAJOR + RX + `ICSALES$` + WPX + `OVERSEAREV$` + VISITORS + JJ + OUTBOUND + NONFUEL + POIL + JPNRX + WTVG + FOOD + TYPH_T + WGP + PCON + PCA + `WGST$` + `VSTOCK$` + NOTERATE + REQ + IR + `DEP$`


train_data <- econ_data %>%
  filter(quarterly_date < train_test_cutoff)
test_data <- econ_data %>%
  filter(quarterly_date >= train_test_cutoff)

taiwan_macro_model <- systemfit(macro_eqn_list, inst = macro_iv_list, method = "2SLS", data = train_data)

taiwan_macro_model_fit <- summary(taiwan_macro_model)

model_formulas <- tibble(formulas = map_chr(taiwan_macro_model_fit$eq, get_model_formula)) %>%
  mutate(formulas = str_replace_all(formulas, "\\$", "^{nominal}")) %>%
  mutate(formulas = paste0("$", formulas, "$")) 

```


***
# Results

## Estimated Coefficients
```{r result_formulae, results="asis"}
model_formulas %>%
  rename(`Estimation Results`=formulas) %>%
  kable("html", escape = TRUE) %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, font_size = 12) %>%
  row_spec(0, bold = TRUE, background = "grey", color = "white") 
```

## RMSE
```{r model_preds}
long_test_data <- test_data %>%
  gather("metric", "value", -quarterly_date) %>%
  mutate(type = "Actual") %>%
  select(quarterly_date, type, metric, value)

taiwan_macro_preds <- predict(taiwan_macro_model, test_data) %>%
  mutate(quarterly_date = test_data$quarterly_date) %>%
  select(quarterly_date, everything()) %>%
  gather("metric", "value", -quarterly_date) %>%
  mutate(metric = toupper(str_replace(metric, "\\.pred", "")),
         type = "Prediction") %>%
  mutate(metric = case_when(metric == "M1BCPI" ~ "M1B_d_CPI",
                            metric == "WG" ~ "WG$",
                            metric == "TAX" ~ "TAX$",
                            metric == "STKVLE" ~ "STKVLE$",
                            TRUE ~ metric)) %>%
  select(quarterly_date, type, metric, value) %>%
  bind_rows(long_test_data) %>%
  spread(type, value) %>%
  filter(!is.na(Prediction)) %>%
  group_by(quarterly_date, metric) %>%
  mutate(RMSE = sqrt(mean((Prediction - Actual)^2)))


```


***
# References