---
title: Building an Initial Macroeconomic Model of Taiwan
author: Travis Dorsey
date: '2020-06-19'
slug: initial-macroeconomic-model-of-taiwan
bibliography: econ_models_bib.bib
biblio-style: "apalike"
nocite: |
  @jp_gnp
  @tfp_dat
  @R-bimets
output:
  blogdown::html_page:
    toc: true
    toc_depth: 2
    number_sections: true
categories: [Econometric Models]
tags:
  - economics
  - data
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)

#################
##  Libraries  ##
#################
library(tidyverse)
library(kableExtra)
library(equatiomatic)
library(systemfit)
library(lubridate)
library(bimets)

options(scipen=999)

econ_vars <- read_csv("/Users/sharedcomputer/MMT in Taiwan/Analysis Replication Files/Macroeconomic Model of Taiwan/New Variable List.csv")


#################
##  Functions  ##
#################

div_replace <- function(model_coef){
  df <- model_coef %>%
    mutate(div_flag = ifelse(str_detect(Variable, "_d_"), 1, 0)) %>%
    mutate(new_Variable = str_split(Variable, "_d_", n = 2)) %>%
    group_by(Variable, div_flag) %>%
    unnest(new_Variable) %>%
    summarize(new_Variable = str_c(new_Variable, collapse = "}{")) %>%
    mutate(new_Variable = ifelse(div_flag == 1, paste0("\\frac{", new_Variable, "}"), new_Variable)) %>%
    ungroup() %>%
    select(Variable, new_Variable)
  
  model_coef <- model_coef %>%
    left_join(df, by = "Variable") %>%
    mutate(Variable = ifelse(is.na(new_Variable), Variable, new_Variable)) %>%
    select(-new_Variable)
  return(model_coef)
}

get_bimets_formulas <- function(bimet_model_list){
  model_coef <- tibble(Variable      = bimet_model_list$eqRegressorsNames,
                       Coefficient   = round(bimet_model_list$coefficients,3),
                       P_values      = bimet_model_list$statistics$CoeffPvalues,
                       R_squared     = bimet_model_list$statistics$RSquared,
                       Adj_R_squared = bimet_model_list$statistics$AdjustedRSquared,
                       Model         = bimet_model_list$lhsFun$raw) %>%
    div_replace() %>%
    mutate(sig_symbol = case_when(Variable == "1" ~ "", 
                                  P_values < 0.001 ~ "(****)",
                                  P_values < 0.01 ~ "(***)",
                                  P_values < 0.05 ~ "(**)",
                                  P_values < 0.1 ~ "(*)",
                                  P_values >= 0.1 ~ "(n.s.)"),
           Variable = str_replace_all(Variable, "_1", "_{-1}")) %>%
    mutate(Variable = ifelse(Variable == "EX_p_C", "EX + C", 
                             ifelse(Variable == "TDR1Y_m_PCHY_CPI", "TDR1Y - \\Delta{CPI}", Variable))) %>%
    mutate(Variable = str_replace_all(Variable, "_nom", "^{nom}"),
           Model    = str_replace_all(Model, "_nom", "^{nom}")) %>%
    mutate(Model = ifelse(Model == "M1B_d_CPI", "\\frac{M1B}{CPI}", Model)) %>%
    mutate(Variable = str_replace_all(Variable, "_p_", "+")) %>%
    mutate(Variable = str_replace_all(Variable, "_m_", "-")) %>%
    mutate(Variable = str_replace_all(Variable, "_x_", "\\*")) %>%
    mutate(new_rhs = ifelse(Variable == "1", 
                            Coefficient, 
                            paste0("\\underset{", sig_symbol, "}{",Coefficient, "*", Variable, "}"))) %>%
    group_by(Model, R_squared, Adj_R_squared) %>%
    summarize(formula = str_c(new_rhs, collapse = " + ")) %>%
    ungroup() %>%
    mutate(formula = paste0("$$", Model, " = ", formula, "$$"))
  return(model_coef)
}

get_bimets_preds <- function(fcast_simulation) {
  fcast_start <- yq(str_c(as.character(start(fcast_simulation)), collapse = "Q"))
  fcast_end   <- yq(str_c(as.character(end(fcast_simulation)), collapse = "Q"))
  
  preds <- tibble(quarterly_date = seq.Date(fcast_start, fcast_end, by = "quarter"),
                  value = as.numeric(fcast_simulation)) %>%
    mutate(type = "Prediction")
  return(preds)
}

```

```{r load_econ_data}
######################
##  Data Wrangling  ##
######################

### Load Datasets
train_test_cutoff <- as_date("2017-01-01")

vars_to_log <- c("C", "YDD$", "STKVLE$", "IBF", "IG", "CAPSTOCK$", "EXS", "OVERSEAREV$", "EXG", "IPC",
                 "JJ", "IMS", "GDP", "VSTOCK$", "GDP$", "DEP$", "EX$", "C$", "COMM_SERVICES", "CULTURE", "ECON_AFFAIRS",
                 "EDU", "ENVIRO_PROTECT", "GEN_PUB_AFFAIRS", "HLTH_INS", "NATL_DEFENSE", "PUB_SAFETY", "SOC_SECURITY",
                 "CG$", "IG$", "IPC$", "IBF$", "JJ$", "GCF$", "EX", "EXG$", "EXS$", "IM", "IMG$", "IMS$", "IM$", "CG",
                 "GCF", "GNI$", "TAX$", "FIA$", "IMG", "M1B", "VISITORS", "OUTBOUND")

rescale_big_vars = FALSE

econ_data_url <- "https://raw.githubusercontent.com/dorseytf/Blog-Replication-Scripts/master/Taiwan%20Macro%20Dataset.csv"
jg_emp_url <- "https://raw.githubusercontent.com/dorseytf/Blog-Replication-Scripts/master/Taiwan%20JG%20Emp%20Dataset.csv"

econ_data <- read_csv(url(econ_data_url))
jg_emp_df <- read_csv(url(jg_emp_url))

if(rescale_big_vars){
  econ_data <- econ_data %>%
    mutate(across(all_of(vars_to_log), rescale_vars))
}

## Create a list of time series objects from each var used
long_econ_data <- econ_data %>%
  gather("metric", "value", -quarterly_date) %>%
  mutate(metric = str_replace_all(metric, "\\$", "_nom")) %>%
  mutate(metric = str_remove_all(metric, "`"))

metric_list <- unique(long_econ_data$metric)

econ_data_list <- vector("list", length = length(metric_list))
for(v in 1:length(metric_list)){
  vals_to_ts <- long_econ_data$value[which(long_econ_data$metric == metric_list[v])]
  start_yr <- min(year(long_econ_data$quarterly_date))
  start_qtr <- min(quarter(long_econ_data$quarterly_date[1]))
  
  econ_data_list[[v]] <- TIMESERIES(vals_to_ts, START = c(start_yr, start_qtr), FREQ = 4)
  names(econ_data_list)[v] <- metric_list[v]
}

```

```{r fit_bimets}
bimets_tol <- 2*10^-24

taiwan_bimets_model <- LOAD_MODEL("/Users/sharedcomputer/MMT in Taiwan/Analysis Replication Files/Taiwan Macro Model v2.txt",
                                  quietly = TRUE)

taiwan_bimets_model <- LOAD_MODEL_DATA(taiwan_bimets_model, econ_data_list, quietly = TRUE)

taiwan_bimets_model <- ESTIMATE(taiwan_bimets_model, 
                                tol = bimets_tol, 
                                quietly = TRUE)

bimet_formula_df <- map_df(taiwan_bimets_model$behaviorals, get_bimets_formulas)

model_name_abbv <- tibble(model_abbv = bimet_formula_df$Model,
                          model_name  = c("Real Private Consumption", "Real Private Fixed Investment",
                                     "Real Exports of Goods and Services",
                                     "Real Imports of Goods and Services",
                                     "Import Price Index", "Export Price Index", 
                                     "Domestic Production Price Index", "Food Consumer Price Index", 
                                     "Non-food Consumer Price Index", "Private Consumption Deflator",
                                     "Government Consumption Deflator", "Private Fixed Investment Deflator",
                                     "Government Fixed Investment Deflator", 
                                     "Public Enterprise Fixed Investment Deflator",
                                     "Gross Capital Formation Deflator", "Exports of Goods and Services Deflator",
                                     "Imports of Goods and Services Deflator", "M1B", "One-Year Fixed Deposit Rate",
                                     "Total Market Capitalization of Listed Stocks", "Number of Employed",
                                     "Monthly Wages per Worker in Industry and Service Sectors", "Tax Revenue"))

print_bimet_formula_df <- bimet_formula_df %>%
  left_join(model_name_abbv, by = c("Model"="model_abbv")) %>%
  mutate(model_name = paste0("**", model_name, "**"),
         R_squared = paste0("$R^{2}: ", round(R_squared, 4), "$"),
         Adj_R_squared = paste0("$Adj. R^{2}: ", round(Adj_R_squared, 4), "$")) %>%
  group_by(Model) %>%
  mutate(third_plus = str_locate_all(formula, "\\+")[[1]][3]) %>%
  mutate(formula = paste(str_sub(formula, 1, third_plus), "\\\\", str_sub(formula, third_plus+1, -1)))

```

Following the methodology laid out by the [Directorate-General of Budget, Accounting, and Statistics](https://www.stat.gov.tw/public/Attachment/6531914262FZ3FA2L.pdf)^[@dgbas_econ], I build an econometric model of Taiwan's macroeconomy that I can utilize to test the impact of policy proposals as in [Fullwiler (2006)](simulating_jg_us).^[@simulating_jg_us] This approach is based on the Cowles Commission methodology of simultaneous equations (similar to the well known [Fairmodel](https://fairmodel.econ.yale.edu/mmm2/mm2018.pdf)^[@fairmodel] used to study the US economy and that of [Lin (2007)](http://www.econ.ntu.edu.tw/ter/new/data/new/TER38-1/TER381-1.pdf)^[@lin_2007_tw_macro] which models the Taiwanese economy) and has been shown to outperform VAR and other time series approaches for macroeconomic forecasts, while also providing a more useful framework for testing policy options than dynamic stochastic generalized equilibrium models, which have [their own issues](https://www.federalreserve.gov/econresdata/ifdp/2016/files/ifdp1175.pdf).^[@frb_dsge] 


***
# Variables and Equations
The model will consist of 25 stochastic equations and 23 identities. The data were compiled from various Taiwanese government agencies, including the Central Bank, the Directorate-General of Budget, Accounting, and Statistics, and the Ministry of Economics. This quarterly dataset covers the period 1997Q2-2018Q4 (87 periods), with the final 8 quarters being used as a holdout sample to test the results of the model fit.

## Variables 

### Endogenous Variables
```{r endog_vars}
econ_vars %>%
  filter(Exogenous == "N") %>%
  select(-c(Description_zh, Exogenous, `Equations Used`)) %>%
  kable('html', align = c("l", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, font_size = 12) %>%
  row_spec(0, bold = TRUE, background = "grey", color = "white") 
```

### Exogenous Variables
```{r exog_vars}
econ_vars %>%
  filter(Exogenous == "Y") %>%
  select(-c(Description_zh, Exogenous, `Equations Used`)) %>%
  kable('html', align = c("l", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, font_size = 12) %>%
  row_spec(0, bold = TRUE, background = "grey", color = "white") 
```


## Equations
Here I show the equations that make up this macroeconometric model of Taiwan. While the methodology laid out in this note from the [Directorate-General of Budget, Accounting, and Statistics](https://www.stat.gov.tw/public/Attachment/6531914262FZ3FA2L.pdf)^[@dgbas_econ] provided a starting point, I have adapted the equations to better handle a quarterly dataset, as well as adding in the hourly minimum wage rate to the formulation for Nominal Monthly Wages per Worker in Industry and Service Sectors to allow for easier testing of policy options later on. 

### Commodity Market
Real Private Consumption (C):
$$
C = f(\underset{+}{C_{-1}}, \underset{+}{\frac{YDD^{nominal}}{PGDP}}, \underset{+}{\frac{STKVLE^{nominal}}{CPI}})
$$
Real Private Fixed Investment (IBF):
$$
IBF = f(\underset{+}{IBF_{-1}}, \underset{+}{IG_{-1}}, \underset{-}{TDR1Y - \Delta(CPI)},\\ \underset{+}{EXG_{-1}},
\underset{+}{\frac{STKVLE^{nominal}}{CAPSTOCK^{nominal}}}, \underset{-}{SPIKE2008})
$$

Real Exports of Goods, Transportation, and Insurance (EXG):
$$
EXG = f(\underset{-}{\frac{PX}{WPX * RX}}, \underset{+}{GDPMAJOR}, \underset{+}{ICSALES^{nominal}},\\
\underset{-}{STEP2008}, \underset{-}{Q1}, \underset{-}{Q2})
$$

Real Other Exports (EXS):
$$
EXS = f(\underset{+}{EXS_{-1}}, \underset{+}{OVERSEAREV^{nominal}},\\ \underset{+}{VISITORS}, \underset{+}{RX}, \underset{-}{Q2}, \underset{+}{Q4})
$$
Real Imports of Goods, Transportation, and Insurance (IMG):
$$
IMG = f(\underset{+}{EXG}, \underset{+}{C}, \underset{+}{IPC + IBF + JJ})
$$
Real Other Imports (IMS):
$$
IMS = f(\underset{+}{IMS_{-1}}, \underset{+}{OUTBOUND})
$$

### Price Indices

Import Price Index (PM):
$$
PM = f(\underset{+}{RX}, \underset{-}{JPNRX}, \underset{+}{NONFUEL},\\ \underset{+}{POIL}, \underset{+}{WPX})
$$

Export Price Index (PX):
$$
PX = f(\underset{+}{PX_{-1}}, \underset{+}{RX}, \underset{+}{PM}, \underset{+}{WTVG})
$$

Domestic Production Price Index (PD):
$$
PD = f(\underset{+}{PD_{-1}}, \underset{+}{PM}, \underset{+}{GDP}, \underset{+}{SPIKE2008})
$$

Food Consumer Price Index (PF):
$$
PF = f(\underset{+}{PF_{-1}}, \underset{+}{FOOD}, \underset{+}{WG^{nominal}_{-1}}, \underset{+}{TYPH_T}, \underset{-}{Q1})
$$
Non-Food Consumer Price Index (PO):
$$
PO = f(\underset{+}{PO_{-1}}, \underset{+}{PM_{-1}}, \underset{+}{PM}, \underset{+}{WG^{nominal}},\\
 \underset{-}{Q1}, \underset{+}{Q2}, \underset{-}{Q3})
$$

Private Consumption Deflator (PC):
$$
PC = f(\underset{+}{PF}, \underset{+}{PO})
$$

Government Consumption Deflator (PCG):
$$
PCG = f(\underset{+}{PCG_{-1}},\underset{+}{PO}, \underset{+}{WGP}, \underset{+}{PIG}, \underset{-}{PD})
$$
Private Fixed Investment Deflator (PIBF):
$$
PIBF = f(\underset{+}{PIBF_{-1}}, \underset{+}{PCON}, \underset{+}{PCA},\\ \underset{+}{WGST^{nominal}}, \underset{-}{SPIKE2008}, \underset{+}{Q1}, \underset{-}{Q2})
$$
Government Fixed Investment Deflator (PIG):
$$
PIG = f(\underset{+}{PIG_{-1}}, \underset{+}{PCON}, \underset{+}{WGST^{nominal}}, \underset{-}{SPIKE2008})
$$

Public Enterprise Fixed Investment Deflator (PIPC)
$$
PIPC = f(\underset{+}{PCON}, \underset{+}{PCA}, \underset{-}{SPIKE2008})
$$

Gross Capital Formation Deflator (PGCF):
$$
PGCF = f(\underset{+}{PCON}, \underset{-}{PCA}, \underset{-}{SPIKE2008})
$$
Exports of Goods and Services Deflator (PEX):
$$
PEX = f(\underset{+}{PX}, \underset{+}{CPI})
$$

Imports of Goods and Services Deflator (PIM):
$$
PIM = f(\underset{+}{PM}, \underset{+}{CPI})
$$

### Financial Money Market
M1B:
$$
M1B = f(\underset{-}{CPI}, \underset{+}{GDP}, \underset{+}{\frac{VSTOCK^{nominal}}{CPI}},\\ \underset{-}{TDR1Y - NOTERATE})
$$

One-year Fixed Deposit Rate (TDR1Y):
$$
TDR1Y = f(\underset{+}{REQ}, \underset{+}{IR}, \underset{+}{GDP_{-1}})
$$

Total Market Capitalization of Listed Stocks (STKVLE$):
$$
STKVLE$ = f(\underset{+}{M1B}, \underset{+}{VSTOCK^{nominal}}, \underset{-}{SPIKE2009})
$$

### Labor Market

Number of Employed (NE):
$$
NE = f(\underset{+}{NE_{-1}}, \underset{-}{\frac{WG^{nominal}}{CPI}}, \underset{+}{GDP})
$$

Monthly Wages per Worker in Industry and Service Sectors (WG$):
$$
WG^{nominal} = f(\underset{+}{MINWGM^{nominal}}, \underset{+}{(GDP^{nom}_{-1} - DEP^{nom}_{-1})}, \\  \underset{+}{Q1}, \underset{-}{DIP2007}, \underset{+}{ELBOW2009})
$$

### Tax Revenues
Tax Revenues (TAX$):
$$
TAX^{nominal} = f(\underset{+}{GDP^{nominal}_{-1}}, \underset{+}{EX^{nominal}+C^{nominal}},\\ \underset{+}{VSTOCK^{nominal}}, \underset{-}{Q1}, \underset{+}{Q2})
$$

## Identities

Nominal Private Consumption (C$):
$$
C^{nominal} = C * \frac{PC}{100}
$$
Nominal Government Consumption (CG$):
$$
CG^{nominal} = Community Services + Culture + \\Economic Affairs + Education + \\Environment Protection + Public Affairs +\\ National Health Insurance + National Defense +\\ Public Safety + Social Security
$$

Real Government Consumption (CG):
$$
CG = \frac{CG^{nom}}{PCG}*100
$$

Real Government Fixed Investment (IG):
$$
IG = \frac{IG^{nom}}{PIG}*100
$$
Real Fixed Investment in Public Enterprises (IPC):
$$
IPC = \frac{IPC^{nom}}{PIPC}*100
$$
Nominal Private Fixed Investment (IBF$):
$$
IBF^{nominal} = IBF * \frac{PIBF}{100}
$$

Nominal Gross Capital Formation (GCF$):
$$
GCF^{nominal} = IG^{nom} + IPC^{nom} + IBF^{nom} + JJ^{nom}
$$
Real Gross Captial Formation (GCF):
$$
GCF = \frac{GCF^{nom}}{PGCF}*100
$$

Real Exports of Goods and Services (EX):
$$
EX = EX_{-1} * (1 + (\frac{\frac{EXG^{nom}_{-1}}{GDP^{nom}_{-1}}* \Delta{EXG} + \frac{EXS^{nom}_{-1}}{GDP^{nom}_{-1}}* \Delta{EXS}}{\frac{EX^{nom}_{-1}}{GDP^{nom}_{-1}}*100}))
$$

Real Imports of Goods and Services (IM):
$$
IM = IM_{-1} * (1 + (\frac{\frac{IMG^{nom}_{-1}}{GDP^{nom}_{-1}}* \Delta{IMG} + \frac{IMS^{nom}_{-1}}{GDP^{nom}_{-1}}* \Delta{IMS}}{\frac{IM^{nom}_{-1}}{GDP^{nom}_{-1}}*100}))
$$
Nominal Exports of Goods and Services (EX$):
$$
EX^{nominal} = EX * \frac{PEX}{100}
$$
Nominal Imports of Goods and Services (IM$):
$$
IM^{nominal} = IM * \frac{PIM}{100}
$$
Nominal Exports of Goods, Transportation, and Insurance (EXG$):
$$
EXG^{nominal} = EX^{nom} * WEIGHTEXG^{nom}
$$
Nominal Imports of Goods, Transportation, and Insurance (IMG$):
$$
IMG^{nominal} = IM^{nom} * WEIGHTIMG^{nom}
$$
Nominal Other Exports (EXS$):
$$
EXS^{nominal} = EX^{nom} - EXG^{nom}
$$
Nominal Other Imports (IMS$):
$$
IMS^{nominal} = IM^{nom} - IMG^{nom}
$$
GDP Growth Rate (PCH GDP):
$$
\Delta{GDP}\% = \frac{C^{nom}_{-1}}{GDP^{nom}_{-1}}*\Delta{C}\% + \frac{CG^{nom}_{-1}}{GDP^{nom}_{-1}}*\Delta{CG}\% + \\
\frac{EX^{nom}_{-1}}{GDP^{nom}_{-1}}*\Delta{EX}\% - \frac{IM^{nom}_{-1}}{GDP^{nom}_{-1}}*\Delta{IM}\%
$$
Real GDP
$$
GDP = C + CG + GCF + EX - IM
$$

Nominal GDP (GDP$):
$$
GDP^{nominal} = C^{nom} + CG^{nom} + GCF^{nom} + EX^{nom} - IM^{nom}
$$
GDP Deflator (PGDP):
$$
PGDP = \frac{GDP^{nom}}{GDP} * 100
$$
Nominal Disposable Income (YDD$):
$$
YDD^{nominal} = GNI^{nom} - DEP^{nom} - TAX^{nom}
$$
Nominal GNI (GNI$):
$$
GNI^{nominal} = GDP^{nom} + FIA^{nom}
$$
Consumer Price Index (CPI):
$$
CPI = CPI_{base} * (0.2972 * \frac{PF}{PF_{base}} + 0.7027 * \frac{PO}{PO_{base}})
$$



***
# Results

## Estimation Results
Below are the results of the system used to model Taiwan's macroeconomy. The significance level of each term is given in parentheses. The R^2 and Adjusted R^2 for each model in the system are also reported. 

Symbol | P-value
------------- | -------------
 (n.s.) | >= 0.1
 (*) | < 0.1
 (**) | < 0.05
 (***) | < 0.01
 (****) | < 0.001
 

```{r result_formulae, results="asis"}

for(i in 1:nrow(print_bimet_formula_df)){
  cat('\n')  
  cat(print_bimet_formula_df$model_name[i], ': \n') 
  cat(print_bimet_formula_df$formula[i], '\n')
  cat(print_bimet_formula_df$R_squared[i], ",", print_bimet_formula_df$Adj_R_squared[i])
  cat('\n')
}

```

## Some Key Takeaways

Some of the most interesting and important things to note from this model include:

1. **Monthly Wages per Worker**: The almost comically large seasonal swings in wage data from Taiwan are actually due to the traditional custom of employers giving out large bonuses (typically the equivalent of 1-2 months worth of wages) leading up to the Lunar New Year celebrations, which fall in Q1 (usually late-January to mid-February).

```{r wage_seasonality}
econ_data %>%
  mutate(qtr = ifelse(quarter(quarterly_date) == 1, "Q1", "Q2-Q4")) %>%
  ggplot(aes(x = quarterly_date, y = `WG$`)) +
  geom_line() +
  scale_y_continuous(labels = scales::dollar) +
  labs(title = "Nominal Monthly Wages per Worker in Taiwan",
       x = "",
       y = "Nominal Monthly Wages (NT$)")
```


2. **Number of Employed**: The original theoretical specification included a Nominal Monthly Wage term which would have a negative coefficient (traditional economic theory suggests wage increases drive down employment). While fitting the model, this term had the expected negative coefficient, but it was not actually significant, which aligns with empirical research on wages that shows that the increase in economic activity that results from wage increases outweigh any marginal employment effects. Therefore, this term was removed.

3. **Real Private Fixed Investment**: The interest rate term is not significant, which also aligns with more modern research that shows firms make investment decisions based mostly on their expectations for future growth, and things like interest rates and tax policy have only limited influence. 


## Predicting on Test Data
Using the holdout sample from Q1 2017 to Q4 2018 we can see that the model performs reasonably well at modeling the various aspects of Taiwan's macroeconomy. 

```{r model_preds}
long_test_data <- econ_data %>%
  filter(quarterly_date >= train_test_cutoff) %>%
  gather("metric", "value", -quarterly_date) %>%
  mutate(type = "Actual") %>%
  select(quarterly_date, type, metric, value)

taiwan_bimets_fcast <- SIMULATE(taiwan_bimets_model,
                                TSRANGE = c(2017,1,2018,4),
                                simConvergence = 0.000001,
                                simIterLimit = 100,
                                simType = "FORECAST",
                                quietly = TRUE)
taiwan_bimets_fcast$simulation[[41]] <- NULL


taiwan_bimets_preds <- vector("list", length = length(taiwan_bimets_fcast$simulation))
for(p in 1:length(taiwan_bimets_preds)){
  taiwan_bimets_preds[[p]] <- get_bimets_preds(taiwan_bimets_fcast$simulation[[p]]) %>%
    mutate(metric = names(taiwan_bimets_fcast$simulation)[p])
}
taiwan_bimets_preds <- bind_rows(taiwan_bimets_preds) %>%
  select(quarterly_date, metric, type, value) %>%
  mutate(metric = str_replace_all(metric, "_nom", "$"))

taiwan_macro_preds <- taiwan_bimets_preds %>%
  bind_rows(long_test_data) %>%
  spread(type, value) %>%
  filter(!is.na(Prediction)) %>%
  group_by(quarterly_date, metric) %>%
  mutate(RMSE = sqrt(mean((Prediction - Actual)^2))) %>%
  gather("type", "value", -c(quarterly_date, metric, RMSE))

taiwan_macro_preds %>%
  filter(metric %in% c("C", "GDP", "WG$", "NE", "STKVLE$", "TAX$")) %>%
  ggplot(aes(x = quarterly_date, y = value, color = type)) +
  geom_line() +
  facet_grid(metric ~ ., scales = "free") +
  scale_color_viridis_d(name = " ") +
  theme(legend.position = "top") +
  labs(title="Performance of Macroeconomic Model for Taiwan",
       x = "",
       y = "")
```


***

# Testing Policy Proposals
With a reasonable model of Taiwan's economy, we can now test various policy proposals to see their impact on the economy.

## Job Guarantee
At the heart of a Job Guarantee (JG) is the promise of a liveable wage for everyone. Most proposals and estimates of the impacts of a JG are based on the US case and use USD\$15/hour liveable wage, however, given that the hourly minimum wage in Taiwan for part-time workers is only ~ USD\$5.32/hour (NT$158 as of Jan-2020), we need to determine a more appropriate wage rate for a Taiwanese Job Guarantee. 

Under Taiwan's current minimum wage system, there is both a Monthly Minimum Wage and an Hourly Minimum Wage to cover full- and part-time workers. These two minimum wage rates are not necessarily tied to each other though, and indeed, in recent years the Hourly Minimum Wage rate has been increased at a faster pace to account for difference in total earnings caused by the difference in hours worked between full- and part-time employees. 

```{r min_wage_yr}
min_wage_url <- "https://raw.githubusercontent.com/dorseytf/Blog-Replication-Scripts/master/Taiwan%20Min%20Wage%20Dataset.csv"

min_wage_monthly <- read_csv(url(min_wage_url))

min_wage_table <- min_wage_monthly %>%
  mutate(Year = year(quarterly_date)) %>%
  filter(Year >= 2005) %>%
  group_by(Year) %>%
  summarize(`Monthly Minimum Wage` = last(MINWGM),
            `Hourly Minimum Wage`  = last(MINWGH)) %>%
  mutate(`Hourly Rate of Monthly Minimum Wage` = paste0("$", round(`Monthly Minimum Wage`/((40*52)/12),1))) %>%
  mutate(`Monthly Minimum Wage` = paste0("$", str_sub(`Monthly Minimum Wage`, 1, 2), ",", 
                                         str_sub(`Monthly Minimum Wage`, 3, -1)),
         `Hourly Minimum Wage` = paste0("$", `Hourly Minimum Wage`)) 
names(min_wage_table)[4] <- paste0(names(min_wage_table)[4], footnote_marker_symbol(1))

min_wage_table %>%
  kable("html", align = c("c", "c", "c", "c"), escape = "F") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, font_size = 12) %>%
  row_spec(0, bold = TRUE, background = "grey", color = "white") %>%
  add_header_above(c("Wage Rates are End of Year values in NT$" = 4), align = "r", background = "white") %>%
  footnote(symbol = c("Hourly Rate of Monthly Minimum Wage is calculated as Monthly Min. Wage / (40 Hours per week * 52 weeks / 12 months)"))
```

Despite the fact that this wage differential is reasonable, given that most people [qualify under the Monthly Minimum Wage](https://www.taiwannews.com.tw/en/news/3523557)^[@twnews_min_wage] and for ease of estimation in this initial model, I will follow the approach used in Tcherneva (2018)^[@tcherneva_jg_design] and set the JG wage rate at the same level for both full- and part-time workers. In future work, I hope to be able to more explicitly model the impacts on full- and part-time workers separately. 

Using a monthly minimum wage of $28,000 (as proposed in various places, including by 3rd Parties [such as the NPP](https://www.facebook.com/newpowerparty/photos/%E6%9C%80%E4%BD%8E%E5%B7%A5%E8%B3%87%E6%87%89%E6%BB%BF%E8%B6%B3%E5%8B%9E%E5%B7%A5%E5%9F%BA%E6%9C%AC%E7%94%9F%E6%B4%BB%E9%9C%80%E8%A6%81%E5%8F%B0%E7%81%A3%E5%8B%9E%E5%8B%95%E5%B8%82%E5%A0%B4%E9%95%B7%E6%9C%9F%E5%AD%98%E5%9C%A8%E4%BD%8E%E8%96%AA%E5%8C%96%E5%95%8F%E9%A1%8C%E8%BF%91%E4%BE%86%E5%84%98%E7%AE%A1gdp%E6%9C%89%E6%89%80%E6%88%90%E9%95%B7%E4%BD%86%E5%AF%A6%E8%B3%AA%E8%96%AA%E5%8D%BB%E4%B8%8D%E6%96%B7%E4%B8%8B%E9%99%8D%E8%B2%A7%E5%AF%8C%E5%B7%AE%E8%B7%9D%E6%8C%81%E7%BA%8C%E6%83%A1%E5%8C%96%E4%BD%BF%E5%BE%97%E6%89%80%E5%BE%97%E5%88%86%E9%85%8D%E4%B8%8D%E5%85%AC%E7%9A%84%E5%95%8F%E9%A1%8C%E6%9B%B4%E7%82%BA%E5%9A%B4%E9%87%8D%E4%BD%8E%E8%96%AA%E7%9A%84%E5%95%8F%E9%A1%8C%E4%B9%9F%E9%80%A3/1028666937204662/)) as the JG wage rate, we can test what impact such a plan would have on Taiwan's economy.

While implementation strategies differ in the literature, we will use a simple 3 year phase-in for the new JG wage rate beginning in 2012 (the full JG wage rate will start in Q1 of 2015). Because a JG is funded by the central government and administered at a local level, the funds for the JG will come from an increase to the Economic Affairs line item of Nominal Government Consumption. 

### Assumptions

1. JG Monthly Wage Rate = $28,000
2. Total costs for the JG program are wages + materials and other costs (an additional 15% of wages)
3. The JG wage rate will be raised gradually to the full $28,000/month with a one-time adjustment each Q1 for 3 years
4. No difference in the JG wage rate between full- and part-time workers
5. Number of Jobs Created

  + **More Conservative Model:** The JG will only hire those who are unemployed, not bring discouraged workers back into the labor force
  + **More Realistic Model:** The JG will hire the unemployed as well as bring discouraged workers back into the labor force (assume 100% of those who would like to work but are not currently looking will be incentivized to join the JG)

```{r jg_forecast}
jg_start_yr <- 2012
jg_phase_in_yrs <- 3
jg_wage_rate <- 28000

#JG Equations
jjg_eqn <- JJG ~ NU * PHASE_NU
wjg_eqn <- WJG ~ WJG_1 + PHASE_WG
yjg_eqn <- YJG ~ JJG*WJG*3 #turn monthly wages into quarterly value
spend_jg_eqn <- SPENDJG ~ YJG + CJG

jg_start_qtr     <- min(econ_data$quarterly_date[which(year(econ_data$quarterly_date) == jg_start_yr)])
jg_phase_end_qtr <- jg_start_qtr + months(33)
jg_phase_in_qtrs <- econ_data$quarterly_date[which(between(econ_data$quarterly_date, jg_start_qtr, jg_phase_end_qtr))]
wg_diff_start_yr <- jg_wage_rate - econ_data$`MINWGM`[which(econ_data$quarterly_date == jg_start_qtr)]
phase_in_addtl   <- wg_diff_start_yr/4

jg_emp_df$PHASE_NU <- 0
for(p in 1:length(jg_phase_in_qtrs)){
  jg_emp_df$PHASE_NU[which(jg_emp_df$quarterly_date %in% jg_phase_in_qtrs)][p] <- round(p*0.0833,2)
}
jg_emp_df <- jg_emp_df %>%
  mutate(PHASE_NU = ifelse(quarterly_date > jg_phase_end_qtr, 1, PHASE_NU)) %>%
  mutate(JJG_cons = NU * PHASE_NU,
         JJG_real = (JOIN_LF+NU) * PHASE_NU)

jg_dataset <- econ_data %>%
  mutate(PHASE_WG = case_when(year(quarterly_date) < jg_start_yr ~ 0,
                              year(quarterly_date) == jg_start_yr ~ phase_in_addtl,
                              year(quarterly_date) == jg_start_yr + 1 ~ 2*phase_in_addtl,
                              year(quarterly_date) == jg_start_yr + 2 ~ 3*phase_in_addtl,
                              year(quarterly_date) >= jg_start_yr + 3 ~ 4*phase_in_addtl,
                              TRUE ~ 0),
         jg_start_MINWGM = MINWGM[which(quarterly_date == jg_start_qtr)],
         `(Intercept)` = 1) %>%
  left_join(jg_emp_df, by = "quarterly_date") %>%
  mutate(WJG          = ifelse(year(quarterly_date) < jg_start_yr, MINWGM, jg_start_MINWGM + PHASE_WG),
         YJG_cons     = ((1000*JJG_cons)*WJG*3)/1000000,
         YJG_real     = ((1000*JJG_real)*WJG*3)/1000000,
         CJG_cons     = 0.15 * YJG_cons,
         CJG_real     = 0.15 * YJG_real,
         SPENDJG_cons = YJG_cons + CJG_cons,
         SPENDJG_real = YJG_real + CJG_real) %>%
  mutate(ECON_AFFAIRS_cons = ECON_AFFAIRS + SPENDJG_cons,
         ECON_AFFAIRS_real = ECON_AFFAIRS + SPENDJG_real,
         NE_cons           = NE + JJG_cons,
         NE_real           = NE + JJG_real) 

long_jg_dataset <- jg_dataset %>%
  gather("metric", "value", -quarterly_date) %>%
  mutate(metric = str_replace_all(metric, "\\$", "_nom")) %>%
  mutate(metric = str_remove_all(metric, "`"))

jg_vars_used <- unique(long_jg_dataset$metric)

jg_data_list <- vector("list", length = length(jg_vars_used))
for(v in 1:length(jg_vars_used)){
  vals_to_ts <- long_jg_dataset$value[which(long_jg_dataset$metric == jg_vars_used[v])]
  start_yr <- min(year(long_jg_dataset$quarterly_date))
  start_qtr <- min(quarter(long_jg_dataset$quarterly_date[1]))
  
  jg_data_list[[v]] <- TIMESERIES(vals_to_ts, START = c(start_yr, start_qtr), FREQ = 4)
  names(jg_data_list)[v] <- jg_vars_used[v]
}

### Conservative JG simulation
# Create TS to adjust NE by the number of ppl employed by JG and MINWGM by the JG Wage phase in
constant_adj_list <- list(NE = TIMESERIES(jg_data_list$JJG_cons['2012-01-01/2018-12-31'], START = c(2012,1), FREQ = 4))

# Adjust ECON_AFFAIRS and MINWGM to reflect JG spending and wage level
taiwan_bimets_model$modelData$ECON_AFFAIRS <- jg_data_list$ECON_AFFAIRS_cons
taiwan_bimets_model$modelData$MINWGM <- jg_data_list$WJG

taiwan_jg_model <- SIMULATE(taiwan_bimets_model,
                            TSRANGE = c(2012, 1, 2018, 4),
                            simType = "FORECAST",
                            simConvergence = 0.0001,
                            simIterLimit = 100,
                            # Exogenize = exogenize_list, 
                            ConstantAdjustment = constant_adj_list,
                            quietly = TRUE)

taiwan_jg_model$simulation[[41]] <- NULL

taiwan_jg_preds <- vector("list", length = length(taiwan_jg_model$simulation))
for(p in 1:length(taiwan_jg_preds)){
  taiwan_jg_preds[[p]] <- get_bimets_preds(taiwan_jg_model$simulation[[p]]) %>%
    mutate(metric = names(taiwan_jg_model$simulation)[p])
}
taiwan_jg_preds <- bind_rows(taiwan_jg_preds) %>%
  select(quarterly_date, metric, type, value) %>%
  mutate(metric = str_replace_all(metric, "_nom", "$"))

long_econ_actuals <- long_econ_data %>%
  filter(quarterly_date >= jg_start_qtr) %>%
  mutate(type = "Actual") %>%
  select(quarterly_date, metric, type, value) %>%
  mutate(metric = str_replace_all(metric, "_nom", "$"))

taiwan_jg_preds_vs_actuals <- taiwan_jg_preds %>%
  bind_rows(long_econ_actuals) %>%
  spread(type, value) %>%
  filter(!is.na(Prediction)) %>%
  group_by(quarterly_date, metric) %>%
  mutate(RMSE = sqrt(mean((Prediction - Actual)^2))) %>%
  gather("type", "value", -c(quarterly_date, metric, RMSE)) %>%
  mutate(type = ifelse(type == "Prediction", "Conservative JG Model", type))

```

```{r jg_realistic_model}
### Realistic JG Simulation
# Create TS to adjust NE by the number of ppl employed by JG and WG$ by the JG Wage phase in
real_constant_adj_list <- list(NE = TIMESERIES(jg_data_list$JJG_real['2012-01-01/2018-12-31'], 
                                               START = c(2012,1), 
                                               FREQ = 4))

# Adjust ECON_AFFAIRS and MINWGM to reflect JG spending and wage level
taiwan_bimets_model$modelData$ECON_AFFAIRS <- jg_data_list$ECON_AFFAIRS_real
taiwan_bimets_model$modelData$MINWGM <- jg_data_list$WJG

taiwan_jg_model_realistic <- SIMULATE(taiwan_bimets_model,
                                      TSRANGE = c(2012, 1, 2018, 4),
                                      simType = "FORECAST",
                                      simConvergence = 0.0001,
                                      simIterLimit = 100,
                                      ConstantAdjustment = real_constant_adj_list,
                                      quietly = TRUE)

taiwan_jg_model_realistic$simulation[[41]] <- NULL

taiwan_jg_preds_realistic <- vector("list", length = length(taiwan_jg_model_realistic$simulation))
for(p in 1:length(taiwan_jg_preds_realistic)){
  taiwan_jg_preds_realistic[[p]] <- get_bimets_preds(taiwan_jg_model_realistic$simulation[[p]]) %>%
    mutate(metric = names(taiwan_jg_model_realistic$simulation)[p])
}
taiwan_jg_preds_realistic <- bind_rows(taiwan_jg_preds_realistic) %>%
  select(quarterly_date, metric, type, value) %>%
  mutate(metric = str_replace_all(metric, "_nom", "$"))

taiwan_jg_preds_vs_actuals_realistic <- taiwan_jg_preds_realistic %>%
  bind_rows(long_econ_actuals) %>%
  spread(type, value) %>%
  filter(!is.na(Prediction)) %>%
  group_by(quarterly_date, metric) %>%
  mutate(RMSE = sqrt(mean((Prediction - Actual)^2))) %>%
  gather("type", "value", -c(quarterly_date, metric, RMSE)) %>%
  mutate(type = ifelse(type == "Prediction", "Realistic JG Model", type))


```



### Results

```{r plot_jg_fcast}
taiwan_jg_preds_vs_actuals %>%
  bind_rows(filter(taiwan_jg_preds_vs_actuals_realistic, type != "Actual")) %>%
  filter(metric %in% c("C", "GDP", "CPI", "NE", "WG$")) %>%
  ggplot(aes(x = quarterly_date, y = value, color = type)) +
  geom_line() +
  facet_grid(metric ~ ., scales = "free") +
  scale_color_viridis_d(name = " ") +
  theme(legend.position = "top") +
  labs(title="Job Guarantee Simulation Results",
       x = "",
       y = "")
```

In addition to increasing employment, implementing a JG in Taiwan would also increase the average monthly wages for everyone in Taiwan by nearly 5%, increase real GDP by approximately 6%, and only increase CPI by 1%, all within the span of a few years. 

*Simulated JG Impacts - Seasonally Adjusted*
```{r jg_results_tbl}
taiwan_jg_preds_vs_actuals %>%
  bind_rows(filter(taiwan_jg_preds_vs_actuals_realistic, type != "Actual")) %>%
  filter(metric %in% c("C", "GDP", "CPI", "NE", "WG$")) %>%
  select(-RMSE) %>%
  spread(type, value) %>%
  group_by(metric, quarterly_date) %>%
  mutate(pct_chg_cons = (`Conservative JG Model` - Actual)/Actual,
         pct_chg_real = (`Realistic JG Model` - Actual)/Actual) %>%
  group_by(metric) %>%
  summarize(`Conservative Model - Change by 2018Q4` = paste0(round(mean(pct_chg_cons[which(quarterly_date == as_date("2018-10-01"))]),3)*100, "%"),
            `Conservative Model - Max Change` = paste0(round(max(pct_chg_cons),3)*100, "%"),
            `Realistic Model - Change by 2018Q4` = paste0(round(mean(pct_chg_real[which(quarterly_date == as_date("2018-10-01"))]),3)*100, "%"),
            `Realistic Model - Max Change` = paste0(round(max(pct_chg_real), 3)*100, "%")) %>%
  kable('html', align = c("l", "c", "c", "c", "c"),
        col.names = c("Metric", "Percent Change in 2018Q4", "2012-2018 Largest Percent Change", 
                      "Percent Change in 2018Q4", "2012-2018 Largest Percent Change")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, font_size = 12) %>%
  add_header_above(c(" " = 1, "Conservative JG Model" = 2, "Realistic JG Model" = 2))
  
```



***
# References