---
title: 'Part 2 Supplement: Mapping Taiwan''s Election Results'
author: Travis Dorsey
date: '2020-05-11'
slug: part-2-supplement-mapping-taiwan-s-election-results
weight: 2.5
output:
  blogdown::html_page:
    toc: true
    toc_depth: 2
    number_sections: TRUE
categories:
  - Proactive Policies for Safeguarding Democracy
tags:
  - data
  - politics
  - populism
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)

#################
##  Libraries  ##
#################
# Load the required libraries
library(flexdashboard)
library(knitr)
library(sp)
library(maptools)
library(mapproj)
library(rgeos)
library(rgdal)
library(broom)
library(purrr)
library(tidyverse)
library(ggrepel)
library(janitor)
library(repmis)

#######################
##  Load Data Files  ##
#######################
#Vote Data
load("/Users/sharedcomputer/MMT in Taiwan/Analysis Replication Files/tw_town_votes.RData")
load("/Users/sharedcomputer/MMT in Taiwan/Analysis Replication Files/tw_county_votes.RData")

#County-level Map
load("/Users/sharedcomputer/MMT in Taiwan/Analysis Replication Files/SCA Data Files/TWshp_county_df.RData")

#Town-level Map
load("/Users/sharedcomputer/MMT in Taiwan/Analysis Replication Files/SCA Data Files/TWshp_town_df.RData")


##########################
##  Setup Mapping Data  ##
##########################
northern_tw <- tibble(county_name = c("臺北市", "新北市", "基隆市", "桃園市", "新竹市", "新竹縣", "宜蘭縣"),
                      county_eng  = c("Taipei City", "New Taipei City", "Keelung City", "Taoyuan City", "Hsinchu City",
                                      "Hsinchu County", "Yilan County"))

central_tw <- tibble(county_name = c("彰化縣", "苗栗縣", "臺中市", "南投縣", "雲林縣"),
                     county_eng  = c("Changhua County", "Miaoli County", "Taichung City", "Nantou County", "Yunlin County"))

southern_tw <- tibble(county_name = c("嘉義縣", "嘉義市", "高雄市", "臺南市", "澎湖縣", "屏東縣"),
                      county_eng  = c("Chiayi County", "Chiayi City", "Kaohsiung City", "Tainan City", "Penghu County", "Pingtung County"))

eastern_tw <- tibble(county_name = c("臺東縣", "花蓮縣"),
                     county_eng  = c("Taitung County", "Hualien County"))

outlying_tw <- tibble(county_name = c("金門縣", "連江縣"),
                      county_eng  = c("Kinmen County", "Lienchiang County"))

outlying_inset <- TWshp_town_df %>%
  filter(county_name %in% outlying_tw$county_name) %>%
  mutate(long = ifelse(county_name == "金門縣", long+1, long),
         lat  = ifelse(county_name == "金門縣", lat, lat-1))

outlying_inset_county <- TWshp_county_df %>%
  filter(county_name %in% outlying_tw$county_eng) %>%
  mutate(long = ifelse(county_name == "Kinmen County", long+1, long),
         lat  = ifelse(county_name == "Kinmen County", lat, lat-1))

outlying_inset_box <- outlying_inset_county %>%
  group_by(county_name) %>%
  summarize(min_x = min(long) - 0.1,
            min_y = min(lat) - 0.1,
            max_x = max(long) + 0.1,
            max_y = max(lat)) 
outlying_inset_box$max_x[which(outlying_inset_box$county_name == "Kinmen County")] <- 119.7
outlying_inset_box$max_y[which(outlying_inset_box$county_name == "Kinmen County")] <- 24.7
outlying_inset_box$max_y[which(outlying_inset_box$county_name == "Lienchiang County")] <- 25.45

tw_town_map_df <- TWshp_town_df %>%
  filter(!county_name %in% outlying_tw$county_name) %>%
  bind_rows(outlying_inset) %>%
  left_join(tw_town_votes, by = c("county_name"="縣市", "town_name"="鄉鎮市區")) 

tw_county_map_df <- TWshp_county_df %>%
  filter(!county_name %in% outlying_tw$county_eng) %>%
  bind_rows(outlying_inset_county) 

theme_bare <- theme(
  axis.line = element_blank(),
  panel.grid.major.x = element_blank(),
  panel.grid.major.y = element_blank(),
  axis.text.x = element_blank(), 
  axis.text.y = element_blank(),
  axis.ticks = element_blank(), 
  axis.title.x = element_blank(), 
  axis.title.y = element_blank(),
  legend.text=element_text(size=7),
  legend.title=element_text(size=16),
  panel.background = element_blank(),
  panel.border = element_rect(colour = "gray", fill=NA, size=0),
  title = element_text(size = 18, face = "bold")
)

TWshp_county <- readOGR(dsn = "/Users/sharedcomputer/MMT in Taiwan/Analysis Replication Files/county map",
                        layer="COUNTY_MOI_1081121",
                        stringsAsFactors = F)
tw_county_labs <- as_tibble(gCentroid(TWshp_county, byid = TRUE)@coords)
tw_county_labs$county_eng <- TWshp_county@data$COUNTYENG

tw_county_labs$y[which(tw_county_labs$county_eng == "New Taipei City")] <- tw_county_labs$y[which(tw_county_labs$county_eng == "New Taipei City")] - 0.05

tw_county_labs$x[which(tw_county_labs$county_eng == "Kinmen County")] <- tw_county_labs$y[which(tw_county_labs$county_eng == "Kinmen County")] + 1

tw_county_labs$x[which(tw_county_labs$county_eng == "Lienchiang County")] <- tw_county_labs$x[which(tw_county_labs$county_eng == "Lienchiang County")] + 1

tw_county_labs$y[which(tw_county_labs$county_eng == "Lienchiang County")] <- tw_county_labs$y[which(tw_county_labs$county_eng == "Lienchiang County")] - 1
```

# Nationwide Election Results
The clearest trend we see from the nationwide results is that the incumbent Tsai Ying-wen won more urban areas, and especially those traditionally associated with a stronger sense of Taiwanese identity (i.e. Tainan and Kaohsiung), by a larger margin. More rural areas, particularly those with larger aboriginal populations and the outlying islands closer to China, voted more heavily for the KMT challenger, Han Kuo-yu.

```{r nation_votes}
ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group, fill = 蔡英文_得票率), 
               data = tw_town_map_df, 
               color = "#d0e8f2", 
               lwd = .01) +
  geom_polygon(aes(x = long, y = lat, group = group), data = tw_county_map_df, color = "black",fill = NA, lwd = .07) +
  geom_rect(data = outlying_inset_box, aes(xmin = min_x, ymin = min_y, xmax = max_x, ymax = max_y), color = "black", fill = NA) +
  scale_fill_viridis_c(name = "Tsai Ying-wen\nVote Share", limits = c(0.1, 0.8)) +
  coord_map(xlim = c(118.4, 122.2), ylim = c(21.7, 25.7)) +
  theme_bare
```

# Regional Breakdown

## Northern Taiwan
```{r north_tw}
north_tw_map <- tw_town_map_df %>%
  filter(county_name %in% northern_tw$county_name) 

north_tw_county <- TWshp_county_df %>%
  mutate_if(is.factor, as.character) %>%
  filter(county_name %in% northern_tw$county_eng)

northern_tw_county_labs <- tw_county_labs %>%
  filter(county_eng %in% northern_tw$county_eng)

north_tw_coord <- north_tw_map %>%
  summarize(min_long = min(long),
            max_long = max(long),
            min_lat  = min(lat),
            max_lat  = max(lat))

north_tw_map %>%
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group, fill = 蔡英文_得票率), 
               color = "#d0e8f2", 
               lwd = .01) +
  geom_polygon(aes(x = long, y = lat, group = group), fill = NA, color = "black", data = north_tw_county) +
  geom_label_repel(data = northern_tw_county_labs, 
                   aes(x = x, y = y, label = county_eng),
                   box.padding   = 0.55, 
                   point.padding = 0.6) +
  scale_fill_viridis_c(name = "Tsai Ying-wen\nVote Share", limits = c(0.1, 0.8)) +
  coord_map(xlim = c(north_tw_coord$min_long-0.2, 122.35), 
            ylim = c(north_tw_coord$min_lat, 25.4)) +
  theme_bare 
```

## Central Taiwan
```{r central_tw}
central_tw_map <- tw_town_map_df %>%
  filter(county_name %in% central_tw$county_name) 

central_tw_county <- TWshp_county_df %>%
  mutate_if(is.factor, as.character) %>%
  filter(county_name %in% central_tw$county_eng)

central_tw_county_labs <- tw_county_labs %>%
  filter(county_eng %in% central_tw$county_eng)

central_tw_coord <- central_tw_map %>%
  summarize(min_long = min(long),
            max_long = max(long),
            min_lat  = min(lat),
            max_lat  = max(lat))

central_tw_map %>%
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group, fill = 蔡英文_得票率), 
               color = "#d0e8f2", 
               lwd = .01) +
  geom_polygon(aes(x = long, y = lat, group = group), fill = NA, color = "black", data = central_tw_county) +
  geom_label_repel(data = central_tw_county_labs, 
                   aes(x = x, y = y, label = county_eng),
                   box.padding   = 0.55, 
                   point.padding = 0.6) +
  scale_fill_viridis_c(name = "Tsai Ying-wen\nVote Share", limits = c(0.1, 0.8)) +
  coord_map(xlim = c(central_tw_coord$min_long-0.2, central_tw_coord$max_long), 
            ylim = c(central_tw_coord$min_lat, central_tw_coord$max_lat)) +
  theme_bare 
```

## Southern Taiwan
```{r south_tw}
southern_tw_map <- tw_town_map_df %>%
  filter(county_name %in% southern_tw$county_name) 

southern_tw_county <- TWshp_county_df %>%
  mutate_if(is.factor, as.character) %>%
  filter(county_name %in% southern_tw$county_eng)

southern_tw_county_labs <- tw_county_labs %>%
  filter(county_eng %in% southern_tw$county_eng)

southern_tw_coord <- southern_tw_map %>%
  summarize(min_long = min(long),
            max_long = max(long),
            min_lat  = min(lat),
            max_lat  = max(lat))

southern_tw_map %>%
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group, fill = 蔡英文_得票率), 
               color = "#d0e8f2", 
               lwd = .01) +
  geom_polygon(aes(x = long, y = lat, group = group), fill = NA, color = "black", data = southern_tw_county) +
  geom_label_repel(data = southern_tw_county_labs, 
                   aes(x = x, y = y, label = county_eng),
                   box.padding   = 0.55, 
                   point.padding = 0.6) +
  scale_fill_viridis_c(name = "Tsai Ying-wen\nVote Share", limits = c(0.1, 0.8)) +
  coord_map(xlim = c(119, southern_tw_coord$max_long), 
            ylim = c(21.7, southern_tw_coord$max_lat)) +
  theme_bare 
```


## Eastern Taiwan
```{r east_tw}
eastern_tw_map <- tw_town_map_df %>%
  filter(county_name %in% eastern_tw$county_name) 

eastern_tw_county <- TWshp_county_df %>%
  mutate_if(is.factor, as.character) %>%
  filter(county_name %in% eastern_tw$county_eng)

eastern_tw_county_labs <- tw_county_labs %>%
  filter(county_eng %in% eastern_tw$county_eng)

eastern_tw_coord <- eastern_tw_map %>%
  summarize(min_long = min(long),
            max_long = max(long),
            min_lat  = min(lat),
            max_lat  = max(lat))

eastern_tw_map %>%
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group, fill = 蔡英文_得票率), 
               color = "#d0e8f2", 
               lwd = .01) +
  geom_polygon(aes(x = long, y = lat, group = group), fill = NA, color = "black", data = eastern_tw_county) +
  geom_label_repel(data = eastern_tw_county_labs, 
                   aes(x = x, y = y, label = county_eng),
                   box.padding   = 0.55, 
                   point.padding = 0.6) +
  scale_fill_viridis_c(name = "Tsai Ying-wen\nVote Share", limits = c(0.1, 0.8)) +
  coord_map(xlim = c(eastern_tw_coord$min_long, eastern_tw_coord$max_long), 
            ylim = c(eastern_tw_coord$min_lat, eastern_tw_coord$max_lat)) +
  theme_bare 
```

## Outlying Islands
```{r lidao_tw}
outlying_tw_map <- tw_town_map_df %>%
  filter(county_name %in% outlying_tw$county_name) 

outlying_tw_county <- tw_county_map_df %>%
  mutate_if(is.factor, as.character) %>%
  filter(county_name %in% outlying_tw$county_eng)

outlying_tw_county_labs <- outlying_inset_box %>%
  select(county_name, min_x, max_x, max_y) %>%
  gather("metric", "value", -county_name) %>%
  mutate(coord = ifelse(str_detect(metric, "_x"), "long", "lat")) %>%
  group_by(county_name, coord) %>%
  summarize(value = mean(value)) %>%
  spread(coord, value) %>%
  mutate(lat = lat + 0.06)

outlying_tw_map %>%
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group, fill = 蔡英文_得票率), 
               color = "#d0e8f2", 
               lwd = .01) +
  geom_polygon(aes(x = long, y = lat, group = group), fill = NA, color = "black", data = outlying_tw_county) +
  geom_rect(data = outlying_inset_box, aes(xmin = min_x, ymin = min_y, xmax = max_x, ymax = max_y), color = "black", fill = NA) +
  geom_label(data = outlying_tw_county_labs, aes(x = long, y = lat, label = county_name)) +
  scale_fill_viridis_c(name = "Tsai Ying-wen\nVote Share", limits = c(0.1, 0.8)) +
  coord_map(xlim = c(118.8, 121), ylim = c(24, 25.7)) +
  theme_bare
```
