---
title: 'Part 1: The Data'
author: Travis Dorsey
date: '2022-04-29'
publishDate: '2022-04-22'
slug: esfc-part-i-the-data
output:
  blogdown::html_page:
    toc: true
    toc_depth: 2
    number_sections: false
categories:
  - Econometric Models
tags:
  - data
  - economics
---

# What Data does an Empirical SFC Model Require?

In the canonical SFC text, [Godley and Lavoie (2012)](https://link.springer.com/book/10.1007/978-1-137-08599-3) use purely theoretical models with numerical simulation. While these work well for exposition and theory purposes, I (and many others) are mostly interested in models based on real world data. This poses a very challenging problem, though, as many of the flows and stocks needed to make a fully consistent and thorough model are not explicitly produced by statistical agencies. But there are ways around this, and any model requires leaving out some level of detail, so it's not the end of the world. 

At a high level, since SFC models are focused on linking the real and financial sides of the economy, we know that we will need all the usual economic variables (GDP, Consumption, Government expenditures, etc.) plus financial data. The latter are usually provided by the Central Bank via the Flow of Funds data. 

With all the data in hand, we can put together an initial balance sheet to determine which sectors and assets will be significant enough to model. 


# An Initial Balance Sheet

As a first step, we take the Consolidated Assets and Liabilities data from [Taiwan's central bank](https://cpx.cbc.gov.tw/Tree/TreeSelect) and calculate each sector's net position (Assets - Liabilities) for each asset.

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
options(scipen=999)

library(tidyverse)
library(janitor)
library(lubridate)
library(kableExtra)

datapath <- "C:/Users/dorse/OneDrive/Documents/Taiwan Research/Taiwan-SFC-Model/Datasets"

raw_balance_sheet_path <- paste(datapath, "Flow of Funds Assets and Liabilities Data.csv", sep="/")

sector_collapse <- tibble(top_sector = c("Private", "Private", "Private", "Private", 
                                         "Public", "Public", "RoW"),
                          sector = c("Households", "Non-Financial Firms", 
                                     "Financial Firms", "Public Enterprises", "Government",
                                     "Central Bank", "Rest of World"))

raw_balance_sheet <- read_csv(raw_balance_sheet_path) %>%
  pivot_longer(cols = -period, names_to = "col_name", values_to = "value") %>%
  rowwise() %>%
  mutate(metric = str_split(col_name, "- ")[[1]][1],
         value_column = str_split(col_name, "- ")[[1]][2],
         sector = str_split(col_name, "- ")[[1]][3]) %>%
  select(year = period, metric, sector, value_column, value) %>%
  distinct() %>%
  pivot_wider(names_from = value_column, values_from = value) %>%
  mutate(sector = ifelse(sector == "Privite enterprises", "Private enterprises", sector),
         sector = ifelse(sector == "Public enterprises", "Public Enterprises", sector))
  
orig_sectors <- unique(raw_balance_sheet$sector)
  
fof_balance_sheet <- raw_balance_sheet %>%
  mutate(sector = case_when(sector == "Households & non-profit institutions" ~ "Households",
                            sector %in% c("Private enterprises") ~ "Non-Financial Firms",
                            sector %in% c("Government", "Central Bank", "Public Enterprises") ~ sector,
                              sector %in% c("Other monetary financial institutions", "Other financial institutions",
                                            "Insurance companies & pension funds") ~ "Financial Firms", 
                              sector == "Rest of the world" ~ "Rest of World")) %>%
  left_join(sector_collapse, by = "sector") %>%
  group_by(year, metric, sector, top_sector) %>%
  summarize(across(where(is.numeric), sum)) %>%
  mutate(net_balance = Assets - Liabilities)
  
rm(raw_balance_sheet)
  
net_lending_by_sector_metric <- fof_balance_sheet %>%
  mutate(net_balance = round(net_balance/1e6, 2)) %>%
  select(-c(Assets, Liabilities, top_sector)) %>%
  pivot_wider(names_from = sector, values_from = net_balance) %>%
  group_by(metric) %>%
  filter(year == max(year))
net_lending_by_sector_metric <- net_lending_by_sector_metric[, c("year", "metric", sector_collapse$sector)]
  
# Add in a column to check that rows sum to 0
row_diffs <- net_lending_by_sector_metric %>%
  pivot_longer(cols = -c(year, metric), names_to = "sector", values_to = "net_balance") %>%
  group_by(year, metric) %>%
  summarize(diff = round(sum(net_balance), 4)) 
  
net_lending_by_sector_metric <- net_lending_by_sector_metric %>%
  left_join(row_diffs, by = c("year", "metric"))
  
# Balance sheet from CB doesn't have bank loans disaggregated by type, so we pull that from statistical bureau
loan_path <- paste0(datapath, "/Monthly Loans Data.csv")

bank_loan_df <- read_csv(loan_path) %>%
  clean_names() %>%
  mutate(metric = str_replace_all(metric, "–", "-")) %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  mutate(`Bank loans - Consumer Credit` = `Bank loans to Consumers - Total` - `Bank loans - Mortgages`) %>%
   pivot_longer(cols = -c(period, units), names_to = "metric", "values_to" = "value") %>%
  filter(!metric %in% c("Bank loans to Consumers - Total", "Construction Loans")) %>%
  mutate(new_period = lubridate::ym(period),
         new_period = ceiling_date(new_period, "month") - days(1),
         period_year = year(new_period))
  
bank_loan_yearly_df <- bank_loan_df %>% 
  group_by(metric, period_year) %>%
  filter(new_period == max(new_period))
  
bank_loans_by_sector <- bank_loan_yearly_df %>%
  filter(period_year == unique(net_lending_by_sector_metric$year)) %>%
  mutate(sector = case_when(str_detect(metric, " - ") ~ "Households",
                            TRUE ~ str_replace(metric, ".*to ", "")),
         sector = str_trim(sector),
         sector = ifelse(sector == "Firms", "Non-Financial Firms", sector),
         value  = round(value/1e6, 2)*-1) %>%
  ungroup() %>%
  select(year = period_year, metric, sector, value) %>%
  mutate(`Financial Firms` = value*-1,
         diff = value + `Financial Firms`) %>%
  pivot_wider(names_from = sector, values_from = value) %>%
  mutate(`Central Bank` = 0,
         `Rest of World` = 0)
bank_loans_by_sector[is.na(bank_loans_by_sector)] <- 0
bank_loans_by_sector <- bank_loans_by_sector[, colnames(net_lending_by_sector_metric)]

# Now add these back to the sectoral balance sheet to identify the assets to model
net_lending_by_sector_metric <- net_lending_by_sector_metric %>%
  bind_rows(bank_loans_by_sector)

```

```{r}
net_lending_by_sector_metric %>%
  rename(Year = year, `Asset Name` = metric) %>%
  kbl(caption = "Net Lending Status by Sector for Taiwan") %>%
  kable_styling(bootstrap_options = c("striped"), full_width = F)
```

A few assets stick out from the table above. Namely,

- 



